Analysis of finite-volume advection schemes on cubed-sphere grids and an accurate \textcolor{red}{scheme} for divergent winds

### 2024-05-21 paper.tex
grid impriting explanation

\textcolor{red}{
One of the major challenges of using grids based on Platonic solids is grid imprinting, which refers to the appearance of grid features on the solution (cf. e.g., \cite{peixoto:2013, weller:2012, mouallem:2023}), and is highly undesirable due to its lack of physical meaning.
In the case of the cubed-sphere, it is expected that undesirable larger errors may appear at the edges of the original cube used to build the cubed-sphere grid.}

@@

The goal of this study is to reassess and suggest enhancements for the current FV3 transport scheme originally developed by \cite{putman:2007}, given its pivotal role in the horizontal dynamics of FV3. 
It is demonstrated that the scheme proposed by \cite{putman:2007} assumes constant metric terms during the application of the PPM to each 1D flux integration domain and employs a first-order departure point calculation for the 1D fluxes.
\textcolor{red}{
The development of a scheme that incorporates a second-order departure point calculation for the 1D fluxes and eliminates the assumption of constant metric terms is proposed.}
While the proposed scheme does not retain the property of splitting error elimination for divergence-free winds and constant scalar fields, it introduces only second-order errors in such scenarios.

@@

Tables  \ref{g2-dx-table} and \ref{g0-dx-table} display the lengths of the  equiangular and equi-edge grids for $N=48\times 2^k$, 
where $k = 0,\ldots, 4$. These values of $N$ are considered in this work.
It can be observed that in terms of length of the cells, the equi-edge grid is less uniform than the equiangular grid.
Despite this, the equi-edge grid is the operational grid in some applications of FV3 \cite{harris:2021,chen:2021}, such as, for instance, 
the Next Generation Global Prediction System (NGGPS) \cite{zhou:2019}, 
because this grid is expected to produce less grid imprinting due to its greater uniformity near the original cube.

>>>>

@@

\textcolor{red}{
Therefore, given the relevance of the FV3 dynamical core,
the goal of this study is to reassess and suggest enhancements for the current FV3 transport scheme originally developed by \cite{putman:2007}, given its pivotal role in the horizontal dynamics of FV3.}
It is demonstrated in this work that the scheme proposed by \cite{putman:2007} assumes constant metric terms during the application of the PPM to each 1D flux integration domain and employs a first-order departure point calculation for the 1D fluxes.
\textcolor{red}{
The development of a scheme that incorporates a second-order departure point calculation for the 1D fluxes and eliminates the assumption of constant metric terms is proposed.}
While the proposed scheme does not retain the property of splitting error elimination for divergence-free winds and constant scalar fields, it introduces only second-order errors in such scenarios.

@@

Tables  \ref{g2-dx-table} and \ref{g0-dx-table} display the lengths of the  equiangular and equi-edge grids for $N=48\times 2^k$, 
where $k = 0,\ldots, 4$. These values of $N$ are considered in this work.
It can be observed that in terms of length of the cells, the equi-edge grid is less uniform than the equiangular grid.
Despite this, the equi-edge grid is the operational grid in some applications of FV3 \cite{harris:2021,chen:2021}, such as, for instance, 
the Next Generation Global Prediction System (NGGPS) \cite{zhou:2019}, 
because this grid is expected to produce less grid imprinting due to its greater uniformity near the original cube.
\textcolor{red}{
Grid imprinting, which refers to the appearance of grid features on the solution (cf. e.g., \cite{peixoto:2013, weller:2012, mouallem:2023}),  is a common problem that appears when using Platonic solid based spherical grids,  and is highly undesirable due to its lack of physical meaning.}
